**Density Dependence**

### 2023-01-10 Rmd/runCond.Rmd
cleaned up

```{r, mac.data}
load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(read_excel(file.path(dropboxdir,"data/inputs/dat.xlsx"),3))
wt =transform(as.data.frame(stock.wt(mac),drop=TRUE),cohort=year-as.numeric(age))
wt =merge(wt,ts,by="year")
wt=ddply(wt,.(age), transform, rsdl =data/mean(data))
wt=ddply(wt,.(age), transform, rsdl_=rsdl/var(data)^0.5)
wt$age=factor(wt$age,levels=sort(unique(wt$age)))
mat=transform(as.data.frame(mat(mac),drop=TRUE),cohort=year-as.numeric(age))
mat=merge(mat,ts)
mat=ddply(mat,.(age), transform, rsdl =data/mean(data))
mat=ddply(mat,.(age), transform, rsdl_=rsdl/var(data)^0.5) 
mat$age=factor(mat$age,levels=sort(unique(mat$age)))
m  =transform(as.data.frame(m(mac),drop=TRUE),cohort=year-as.numeric(age))  
m  =merge(m,ts)
m  =ddply(m,.(age), transform, rsdl =data/mean(data))
m  =ddply(m,.(age), transform, rsdl_=rsdl/var(data)^0.5) 
m$age=factor(m$age,levels=sort(unique(m$age))) 
```

@@

fn<-function(x,dat) 
   sum((dat$mat-matFn(x,dat$wt))^2)

@@

par$par

ggplot(dat,aes(wt,mat))+
  geom_point(aes(wt,mat,col=age))+
  geom_smooth(se=F,span=0.2)+
  xlab("Age")+ylab("Matutrity")+
  geom_line(aes(wt,mat),col="red",data=data.frame(mat=matFn(dat$wt,par$par),wt=dat$wt))
```

**Figure `r iFig=iFig+1; iFig`** Maturity-at-age v mass-at-age

```{r}
gmr=gammV(data~s(tb, bs="tp")+age, data=wt)
summary(gmr)
plot(gmr)
```

@@

```{r, whb.data}
load(file.path(dropboxdir,"data/om/whb.RData"))
ts=model.frame(FLQuants(whb,tb=biomass,ssb=ssb),drop=T)
ts$tb=ts$tb/1e6
wt =transform(as.data.frame(stock.wt(whb),drop=TRUE),cohort=year-as.numeric(age))
wt =merge(wt,ts,by="year")
wt=ddply(wt,.(age), transform, rsdl =data/mean(data))
wt=ddply(wt,.(age), transform, rsdl_=rsdl/var(data)^0.5)
wt$age=factor(wt$age,levels=sort(unique(wt$age)))
mat=transform(as.data.frame(mat(whb),drop=TRUE),cohort=year-as.numeric(age))
mat=merge(mat,ts)
mat=ddply(mat,.(age), transform, rsdl =data/mean(data))
mat=ddply(mat,.(age), transform, rsdl_=rsdl/var(data)^0.5) 
mat$age=factor(mat$age,levels=sort(unique(mat$age)))
m  =transform(as.data.frame(m(whb),drop=TRUE),cohort=year-as.numeric(age))  
m  =merge(m,ts)
m  =ddply(m,.(age), transform, rsdl =data/mean(data))
m  =ddply(m,.(age), transform, rsdl_=rsdl/var(data)^0.5) 
m$age=factor(m$age,levels=sort(unique(m$age)))
```

@@

ggplot(dat,aes(wt,mat))+
  geom_point(aes(wt,mat,col=age))+
  geom_smooth(se=F,span=0.2)+
  xlab("Age")+ylab("Matutrity")+
  geom_line(aes(wt,mat),col="red",data=data.frame(mat=matFn(dat$wt,par$par),wt=dat$wt))
```

```{r}
gmr=gammV(data~s(tb)+age, data=wt)
summary(gmr)
plot(gmr)
```

>>>>

```{r, mac.data}
load(file.path(dropboxdir,"data/om/mac.RData"))
ts =as.data.frame(read_excel(file.path(dropboxdir,"data/inputs/dat.xlsx"),3))
wt =transform(as.data.frame(stock.wt(mac),drop=TRUE),cohort=year-as.numeric(age))
wt =merge(wt,ts,by="year")
wt=ddply(wt,.(age), transform, rsdl =data/mean(data))
wt=ddply(wt,.(age), transform, rsdl_=rsdl/var(data)^0.5)
wt$age=factor(wt$age,levels=sort(unique(wt$age)))

mat=transform(as.data.frame(mat(mac),drop=TRUE),cohort=year-as.numeric(age))
mat=merge(mat,ts)
mat=ddply(mat,.(age), transform, rsdl =data/mean(data))
mat=ddply(mat,.(age), transform, rsdl_=rsdl/var(data)^0.5) 
mat$age=factor(mat$age,levels=sort(unique(mat$age)))

m  =transform(as.data.frame(m(mac),drop=TRUE),cohort=year-as.numeric(age))  
m  =merge(m,ts)
m  =ddply(m,.(age), transform, rsdl =data/mean(data))
m  =ddply(m,.(age), transform, rsdl_=rsdl/var(data)^0.5) 
m$age=factor(m$age,levels=sort(unique(m$age))) 
```

@@

@@

ggplot(dat,aes(wt,mat))+
  geom_point(aes(wt,mat,col=age))+
  geom_smooth(se=F,span=0.2)+
  xlab("Mass-at-age")+ylab("Matutrity-at-age")+
  geom_line(aes(wt,mat),col="red",data=data.frame(mat=matFn(dat$wt,par$par),wt=dat$wt))
```

**Figure `r iFig=iFig+1; iFig`** Maturity-at-age v mass-at-age  (k=`r par$par[1]` $W_{50}$=`r par$par[2]`)

```{r}
wt=subset(wt,age!=0)
gmr=gammV(log(data)~s(tb/mean(tb), bs="tp")+age, data=wt)
summary(gmr)
plot(gmr)
coefficients(gmr)

wt=cbind(wt,hat=predict(gmr))

plot(exp(coefficients(gmr)[2:12]))
wt=merge(wt,data.frame(age=1:12,mean=exp(c(0,coefficients(gmr)[2:12]))))

ggplot(wt)+
  geom_line(aes(tb,exp(hat)/mean,col=age))+
  geom_point(aes(tb,data/mean,col=age))+
  xlab("Biomass")+ylab("Mass-Mean")

summary(lm(hat~tb,data=transform(wt,tb=tb/mean(tb))))
```

@@

```{r, whb.data}
load(file.path(dropboxdir,"data/om/whb.RData"))
ts=model.frame(FLQuants(whb,tb=stock,ssb=ssb),drop=T)
ts$tb=ts$tb/1e6
wt =transform(as.data.frame(stock.wt(whb),drop=TRUE),cohort=year-as.numeric(age))
wt =merge(wt,ts,by="year")
wt=ddply(wt,.(age), transform, rsdl =data/mean(data))
wt=ddply(wt,.(age), transform, rsdl_=rsdl/var(data)^0.5)
wt$age=factor(wt$age,levels=sort(unique(wt$age)))

mat=transform(as.data.frame(mat(whb),drop=TRUE),cohort=year-as.numeric(age))
mat=merge(mat,ts)
mat=ddply(mat,.(age), transform, rsdl =data/mean(data))
mat=ddply(mat,.(age), transform, rsdl_=rsdl/var(data)^0.5) 
mat$age=factor(mat$age,levels=sort(unique(mat$age)))

m  =transform(as.data.frame(m(whb),drop=TRUE),cohort=year-as.numeric(age))  
m  =merge(m,ts)
m  =ddply(m,.(age), transform, rsdl =data/mean(data))
m  =ddply(m,.(age), transform, rsdl_=rsdl/var(data)^0.5) 
m$age=factor(m$age,levels=sort(unique(m$age)))
```

@@

ggplot(dat,aes(wt,mat))+
  geom_point(aes(wt,mat,col=age))+
  geom_smooth(se=F,span=0.2)+
  xlab("Mass-at-age")+ylab("Matutrity-at-age")+
  geom_line(aes(wt,mat),col="red",data=data.frame(mat=matFn(dat$wt,par$par),wt=dat$wt))
```

**Figure `r iFig=iFig+1; iFig`** Maturity-at-age v mass-at-age  (k=`r par$par[1]` $W_{50}$=`r par$par[2]`)

```{r}
gmr=gammV(log(data)~s(tb, bs="tp")+s(year, bs="tp")+age, data=wt)
summary(gmr)
plot(gmr)
coefficients(gmr)

wt=cbind(wt,hat=predict(gmr))

plot(coefficients(gmr)[2:10])
wt=merge(wt,data.frame(age=1:10,mean=c(0,coefficients(gmr)[2:10])))

p=ggplot(wt)+
  geom_line(aes(tb,exp(hat-mean),col=age))+
  geom_point(aes(tb,data-exp(mean),col=age))+
  xlab("Biomass")+ylab("Mass-Mean")
```

```{r}
wt =transform(as.data.frame(stock.wt(whb),drop=TRUE),cohort=year-as.numeric(age))
wt =merge(wt,ts,by="year")
wt=ddply(wt,.(age), transform, rsdl =data/mean(data))
wt=ddply(wt,.(age), transform, rsdl_=rsdl/var(data)^0.5)
wt$age=factor(wt$age,levels=sort(unique(wt$age)))

wt=subset(wt,age!=0)
gmr=gammV(log(data)~s(tb/mean(tb), bs="tp")+age, data=wt)
summary(gmr)
plot(gmr)
coefficients(gmr)

wt=cbind(wt,hat=predict(gmr))

plot(exp(coefficients(gmr)[2:12]))
wt=merge(wt,data.frame(age=1:12,mean=exp(c(0,coefficients(gmr)[2:12]))))

ggplot(wt)+
  geom_line(aes(tb,exp(hat)/mean,col=age))+
  geom_point(aes(tb,data/mean,col=age))+
  xlab("Biomass")+ylab("Mass-Mean")

summary(lm(hat~tb,data=transform(wt,tb=tb/mean(tb))))
```

### 2023-01-10 Rmd/runDD.Rmd
cleaned up

---
title: "**Density Dependence**"
subtitle: "Example of modellimng density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE

@@

Mackerel life history parameters are used to construct an `FLBRP` object to represent the equilibrium dynamics and then an `FLStock` object models the time series dynamics.

@lorenzen2000allometry noted that theoretical and empirical studies point to the existence of an allometric relationship between natural mortality $M_a$ and body mass ($W_a$) at-age in fish of the form:

  $M_a \propto {W_a}^{d}$

i.e.

@@

where $M_W$ is $M$ at weight $W$, $M_u$ is $M$ at unit weight, and $d$ is the allometric exponent from empirical relationships shown to range from –0.3 to –0.37, e.g. if $M_t=0.2$ at a weight when $50\%$ of individuals reach maturity $W_{50}$ then

  $M_u = 0.2/({W_{50}}^{d})$

Since weight is approximately proportional to the third power of length  values of $d$ of approximately –1/3 imply that $M$ is inversely proportional to body length. @10.1093/icesjms/fst226 recognised that for ($L$) if the von Bertalanffy and length–weight parameters are known, then the mortality schedule can be defined by

where $L_{\infty}$ is the asmypotopic length,  $k$ growth rate, and $t_0$ is the age at which length is zero of the von Bertalanffy growth equation,  and the allometric relationship $W = a L^b$.

This gives

$M_t = M_{\infty}{(W_t/W_{\infty})}^{-0.3}$

where $M_t$ is the instantaneous $M$ rate per year at age $t$ and $M_{\infty}$ is the asymptotic $M$ rate at the asymptotic weight $W_{\infty}$, derived from life history characteristics @hoenig1992empirical

$M2(L^\prime) = \Omega \times UM2(L^\prime)^{(\kappa + \lambda)} e^{(\mu((\kappa + \lambda)/3))} \times e^{({\sigma}^2((\kappa+\lambda)^2)/18)}$

@@

```{r}
ddWt<-function(wt,biomass, bmsy)
  wt%*%qmax((biomass/bmsy)^0.3,0.5)

matFn<-function(wt,x) 
   1/(1+exp(-x[1]*(wt-x[2])))

ddFn<-function(year,x,par){
  lsr=landings.wt(x)[,year]/stock.wt(x)[,year]
  dsr=discards.wt(x)[,year]/stock.wt(x)[,year]

  stock.wt(   x)[,year]=ddWt(stock.wt(x)[,year],biomass(x)[,ac(an(year)-1)],par["bmsy"])
  landings.wt(x)[,year]=stock.wt(x)[,year]*lsr
  discards.wt(x)[,year]=stock.wt(x)[,year]*dsr

  mat(x)[,year]=matFn(stock.wt(x)[,year],par[c("k","w50")])
  m(  x)[,year]=par["m1"]%*%(stock.wt(x)[,year]%^%par["m2"])

  fwd(x,f=f[,year],sr=eq)}
```

@@

# Sumulations

@@

```{r}
plot(qmax((biomass(eq)%/%biomass(eq)[,c(14)])^0.3,0.5))+
  scale_y_continuous(labels = scales::percent)+
  geom_vline(aes(xintercept=14),col="red")+
  xlab("Biomass")+ylab("% Change in mass-at-age")
```

@@

```{r}
wt=ddWt(stock.wt(eq),biomass(eq),refpts(eq)["msy","biomass"])

ggplot(as.data.frame(wt))+           
    geom_line(aes(age,data,col=factor(year)))+
    theme(legend.position="none")+
    scale_x_continuous(limits=c(0,15))+
    xlab("Age")+ylab("Mass-at-age")
```

@@

@@

**Figure `r iFig=iFig+1; iFig`** Simulation of density dependence in M-at-age

@@

```{r}
x=propagate(eq,length(dimnames(eq)$year))
fbar(x)=fbar(x)[,1]
fbar(x)=c(fbar(eq))

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(20)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"])
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr
  x=brp(x)}

@@

```{r}
x=propagate(eq,length(dimnames(eq)$year))
fbar(x)=fbar(x)[,1]
fbar(x)=c(fbar(eq))

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(20)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"])
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr

@@

```{r}
x=propagate(eq,length(dimnames(eq)$year))
fbar(x)=fbar(x)[,1]
fbar(x)=c(fbar(eq))

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(20)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"])
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr

@@

om2=om
for (year in dimnames(om2)$year[-1]){
#  lsr=landings.wt(om2)[,year]/stock.wt(om2)[,year]
#  dsr=discards.wt(om2)[,year]/stock.wt(om2)[,year]

#  stock.wt(   om2)[,year]=ddWt(stock.wt(om2)[,year],biomass(om2)[,ac(an(year)-1)],par["bmsy"])
#  landings.wt(om2)[,year]=stock.wt(om2)[,year]*lsr
#  discards.wt(om2)[,year]=stock.wt(om2)[,year]*dsr

#  mat(om2)[,year]=1/(1+exp(-par["k"]*(stock.wt(om2)[,year]-par["w50"])))
#  m(  om2)[,year]=par["m1"]%*%(stock.wt(om2)[,year]%^%par["m2"])

#  om2=fwd(om2,f=f[,year],sr=eq)

@@

>>>>

---
title: "**Density Dependence**"
subtitle: "Example of modelling density dependence in mass, maturity and M-at-age"
author: "L Kell"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: html_document
mathjax: TRUE

@@

Mackerel life history parameters are used to construct an example of modelling density dependence. An `FLBRP` object represents the equilibrium and an `FLStock` models the time series dynamics.

### Mass-at-age

Mass-at-age ($W_a$) is modelled as

$W_a = {\alpha}_a B^{{\beta}_a}$

Where $\alpha$ and $\beta$ are taken from a linear regression of Mass~Total biomass, i.e. we model mass-at-age at each age based on empirical data.

$W_a$ is also constrained so sizes do not become unfeasibly small or large

### Predation mortality-at-age (M2)

#### Pope

@pope2006modelling (doi:10.1016/j.icesjms.2006.04.015) proposed a way of modelling predation mortality (M2) based on size spectra, by modelled $M$ as a function of length i.e.

$M2(L)=\gamma(F) e^{\lambda(F) L}$

where Where $\gamma=2.0753+0.9914F$ and $\lambda = −0.0276−0.1088F$ and $F$ is fishing mortality

However, the model is in mass-at-age, so we convert $L$ to $W$

$M2(L)=\gamma(F) e^{\lambda(F) (W/a)^{1/b}}$

$\gamma$ is scaled so that M at at reference length is equal to a desired value.

A problem is that this will formulation respond immediately to a change in F. However, the size spectra depends on the historical not the current $F$. For example, for a specific value of $F$ in the current year, if the stock as been subject to a period of heavy exploitation the size spectra will be very different to that of a virgin fishery in the first year of exploitation. This will create problems in simulations of management as in an MSE.

#### Lorenzen

Theoretical and empirical studies [@lorenzen2000allometry] support the existence of an allometric relationship between natural mortality ($M_a$) and body mass ($W_a$) at age of the form:

@@

where $M_W$ is $M$ at weight $W$, $M_u$ is $M$ at unit weight, and $d$ is the allometric exponent from empirical relationships shown to range from –0.3 to –0.37.

If $M=0.2$ at $W_{50}$ then $M_u = 0.2/({W_{50}}^{d})$

$d$ is approximately equal to $–1/3$, which implies that $M$ is inversely proportional to body length., since mass is approximately proportional to the third power of length.

### Maturity-at-weight

Modelled as a logistic function of mass-at-age e.g.

$O(W) = 1/(1+e^(k(W-W50)))$

## Sparholt, empirical

Mackerel

$M = 0.0232 * TB + 0.0524$

Blue whiting:

$M = 0.0221 * TB  + 0.0719$

@@

```{r}
source("../R/dd.R")
```

@@

# Simulations

@@

```{r}
plot(qmin(qmax(0.96*biomass(eq)%/%biomass(eq)[,14],0.5),1.5))+
  scale_y_continuous(labels = scales::percent)+
  geom_vline(aes(xintercept=14),col="red")+
  xlab("Biomass")+ylab("% Change in mass-at-age")
```

@@

```{r}
save(eq,file="~/Desktop/eq.RData")
```

```{r}
wt=ddWt(stock.wt(eq),biomass(eq),refpts(eq)["msy","biomass"]) 
ggplot(as.data.frame(wt))+           
    geom_line(aes(age,data,col=factor(year)))+
    theme(legend.position="none")+
    scale_x_continuous(limits=c(0,15))+
    xlab("Age")+ylab("Mass-at-age") 
```

@@

```{r}
ggplot(ddM(stock.wt(eq),fbar(eq)))+
    geom_line(aes(age,data,col=factor(year)))+
    theme(legend.position="none")+
    scale_x_continuous(limits=c(0,15))+
    xlab("Age")+ylab("M-at-age") 
```

**Figure `r iFig=iFig+1; iFig`** Pope: simulation of density dependence in M-at-age

@@

**Figure `r iFig=iFig+1; iFig`** Lorenzen: Simulation of density dependence in M-at-age

@@

```{r, dd-eq-mass}
x=propagate(eq,length(dimnames(eq)$year))
fbar(x)=fbar(x)[,1]
fbar(x)[]=c(fbar(eq))*2

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(10)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"],alpha=-0.17)
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr
  x=brp(x)}

@@

```{r, dd-eq-mass-mat}
x=propagate(eq,length(dimnames(eq)$year))
fbar(x)[,1]=c(seq(0,max(fbar(eq)),length.out=51),seq(1,50,length.out=51)*max(fbar(eq)))[-52]
fbar(x)=fbar(x)[,1]

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(10)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"],alpha=-0.17)
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr

@@

```{r, dd-eq-mass-mat-m}
x=propagate(eq,length(dimnames(eq)$year))
fbar(x)[,1]=c(seq(0,max(fbar(eq)),length.out=51),seq(1,50,length.out=51)*max(fbar(eq)))[-52]
fbar(x)=fbar(x)[,1]

lsr=landings.wt(eq)/stock.wt(eq)
dsr=discards.wt(eq)/stock.wt(eq)
# iterate
for (i in seq(10)){
  stock.wt(   x)=ddWt(stock.wt(eq),biomass(x),refpts(eq)["msy","biomass"],alpha=-0.17)
  landings.wt(x)=stock.wt(x)*lsr
  discards.wt(x)=stock.wt(x)*dsr

@@

om2=om
lsr=landings.wt(om2)/stock.wt(om2)
dsr=discards.wt(om2)/stock.wt(om2)

for (year in dimnames(om2)$year[-1]){

  #stock.wt(   om2)[,year]=ddWt(stock.wt(om2)[,year],biomass(om2)[,ac(an(year))],par["bmsy"])
  #landings.wt(om2)[,year]=stock.wt(om2)[,year]*lsr[,year]
  #discards.wt(om2)[,year]=stock.wt(om2)[,year]*dsr[,year]

  #mat(om2)[,year]=1/(1+exp(-par["k"]*(stock.wt(om2)[,year]-par["w50"])))
  #m(  om2)[,year]=par["m1"]%*%(stock.wt(om2)[,year]%^%par["m2"])

  #om2=fwd(om2,f=f[,year],sr=eq)}

@@

## Mackerel

Mass-at-age

$W_a = \alpha_aB+\beta$

<!-- $M = ~~0.0232 \times B + 0.0524$ -->

Predation mortality-at-age

$M_2(L) =ae^{bL}$

where $a=2.0753+0.9914F$ and $b=-0.0276-0.1088F$

Maturity-at-weight

$O(W) = \frac{1}{1+e^{-1.67(W-28.2)}}$

## Blue whiting:

$M = 0.0221 \times B   + 0.0719$

## Mass-at-age

Individual mass-at-age is assumed to vary with total biomass, estimates of mass-at-age (${W_t}^\prime$) are based on observations around $B_{MSY}$, and if total biomass increases density dependence results in a decline in the expected value of $W_a$, i.e.

$W_t = {W_t}^\prime a(B_t/B_{MSY})^b$

## Maturity-at-age

Maturity at age is modelled by a logistic relationship

$f(x) = \frac{1}{1+e^{-r(W-W_{50})}}$

where $W_{50}$ is the mass-at-age when $50%$ of individuals are mature, and $r$ the logistic growth rate or steepness of the curve.

Theoretical and empirical studies [@lorenzen2000allometry] support the existence of an allometric relationship between natural mortality ($M_a$) and body mass ($W_a$) at age of the form:

where $M_W$ is $M$ at weight $W$, $M_u$ is $M$ at unit weight, and $d$ is the allometric exponent from empirical relationships shown to range from –0.3 to –0.37.

If $M=0.2$ at $W_{50}$ then $M_u = 0.2/({W_{50}}^{d})$

$d$ is approximately equal to $–1/3$, which implies that $M$ is inversely proportional to body length., since mass is approximately proportional to the third power of length.

@10.1093/icesjms/fst226 recognised that if the von Bertalanffy growth equation

and the allometric length weight relationship

$W = a L^b$.

are combined since

$M_a = M_{\infty}{(W_a/W_{\infty})}^{-0.3}$

then mortality schedule can be defined by

$M_a=M_{\infty}(1−e^{(−K(t−t_0))})^{−b(0.3)}$

where $M_{\infty}$ can be derived from life history characteristics @hoenig1992empirical

$M2(L^\prime) = \Omega \times UM2 (L^\prime)^{(\kappa + \lambda)}\times e^{\mu((\kappa + \lambda)/3)} \times e^{{\sigma}^2((\kappa+\lambda)^2)/18}$

This simplifies to

$M2(L) = aL^b$

and is therefore equivalent to

depending on the choice of $a$ and $b$
